Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 interviews.tex
remove reference to case study

Integrating R also helps Jyothi's topic modeling tool, described in the
last section: ``Having an open session where I can run R commands or R
functions without having to invoke an API or send out a request and then
wait for the request to come back [...] is extremely helpful in writing the
application.''

>>>>

Integrating R also helps Jyothi's application: ``Having an open session
where I can run R commands or R functions without having to invoke an API
or send out a request and then wait for the request to come back [...] is
extremely helpful.''
